---
title: "Lab 10"
author: "Brad McNeney"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

The folder `Lab10Data contains several CSV data files.

```{r}
dfiles <- dir("Lab10Data",full.names=TRUE)
dfiles
```

1. Write R code to read in the first file.
Print the tibble that you just read in.
Use `names()` to change the column names of the
tibble to `x` and `y`.
Repeat for the second file. How many observations
are in these first two files?
```{r}
study1 <- read_csv("Lab10Data/study1.csv")
names(study1) <- c("x","y")

study2 <- read_csv("Lab10Data/study2.csv")
names(study2) <- c("x","y")
```

2. Use `vector()` to create an empty vector 
called `ff` that is of mode "list" and length 9.
Now write a `for()` loop to loop over the 9 files in
`dfile` and for each (i) read the file in to a 
tibble, and change the column names to 
`x` and `y` as in part (1), and  (ii) copy the 
tibble to an element of your list `ff`.

```{r}
ffunc <- function(file){
  localff <- vector(mode="list", length = 9)
  for(i in 1:9){
    readdfile<-read_csv(file[i])
    names(readdfile) <- c("x","y")
    localff[[i]]<-readdfile
  }
  return(localff)
}
ff <- ffunc(dfiles)
```


3. Write a function called `read.study_data`
that takes a vector of data file
names (like `dfile`) as input, reads the data files
into a list, assigns class "study_data" to the list,
and returns the list. Your function should use `length(dfile)`
to determine the number of files.
```{r}
read.study_data <- function(file){
  len=length(file)
  localff <- vector(mode="list", length = len)
  for(i in 1:len){
    readdfile<-read_csv(file[i])
    localff[[i]]=readdfile
  }
  class(localff)="study_data"
  return(localff)
}
ff2<-read.study_data(dfiles)
```


4. Write a function `plot.study_data()` that 
takes an object of class "study_data" as input.
The first 5 lines of your function should be the
following, which creates a tibble  with
columns `study`, `x` and `y`:
```{r,eval=FALSE}
  dat <- NULL
  for(i in seq_along(ff)) {
    d <- ff[[i]]
    dat <- rbind(dat,tibble(study=i,x=d$x,y=d$y))
  }
```
Have your function coerce `study` to a factor, and then call
`ggplot()` to make a plot of `y` *versus* `x`,
with different colours for the different studies.
Add points and smoothers to your plot.

